%-------------------------
% Stepanenko Nazar — Full-Stack / Web Developer CV
% Based on Jake's Resume template (https://github.com/jakegut/resume)
% License: MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{xcolor}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Accent color — slightly different to differentiate
\definecolor{accent}{HTML}{0A6E47}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries\color{accent}
}{}{0em}{}[\color{accent}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Stepanenko Nazar} \\ \vspace{4pt}
    \small {\color{accent}\textbf{Full-Stack / Web Developer (Junior)}} \\ \vspace{4pt}
    \faMapMarker* \, Kyiv, Ukraine \quad
    \faEnvelope \, \href{mailto:gangsterstepa@gmail.com}{gangsterstepa@gmail.com} \quad
    \faGithub \, \href{https://github.com/d3Par1}{github.com/d3Par1} \quad
    \faLinkedin \, \href{https://www.linkedin.com/in/yourhandle}{LinkedIn} \quad
    \faTelegram \, @yourhandle
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small
Computer Science student (2nd year, Igor Sikorsky KPI) building production-style full-stack web applications with Node.js, Express, and modern frontend tooling. Recently shipped a finance-management web app as a team coursework, plus several side projects in Python (Telegram bots), Lua (Roblox), and 3D content (Blender). Looking for an internship or working-student role to grow as a full-stack engineer in a product-driven team.
\vspace{-6pt}

%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: JavaScript / Node.js, Python, C\#, C / C++, Lua, SQL, HTML, CSS} \\
     \textbf{Web \& Backend}{: Express.js, REST API design, EJS, Bootstrap 5, Chart.js, SQL (SQLite) schema design, Authentication (bcrypt, sessions), Async Python (asyncio, aiogram)} \\
     \textbf{Tools \& Workflow}{: Git / GitHub, GitHub Actions (basic), npm / pnpm, VS Code, Postman, Docker (basic), Linux (CLI, Bash), Blender (3D content)} \\
     \textbf{Domain Interest}{: SaaS, fintech, dev tools, productivity products, e-commerce}
    }}
\end{itemize}
\vspace{-16pt}

%-----------LANGUAGES-----------
\section{Spoken Languages}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item
        Ukrainian (Native) \quad\textbullet\quad
        English (Advanced \textbf{C1}) \quad\textbullet\quad
        French (Intermediate \textbf{B1--B2}) \quad\textbullet\quad
        German (Beginner \textbf{A1--A2})
    }
\end{itemize}
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Personal Finance Manager} $|$ \emph{Node.js, Express, SQLite, Bootstrap, EJS, Chart.js}}{2026}
    \resumeItemListStart
      \resumeItem{Designed and implemented authentication module (bcrypt + sessions), multi-account architecture, REST API.}
      \resumeItem{Built interactive analytics dashboard with Chart.js — multi-series time-series visualization with server-side aggregation via SQL \texttt{GROUP BY}.}
      \resumeItem{Designed relational schema covering users, accounts, transactions, categories with referential integrity.}
      \resumeItem{Team project (2 engineers); owned auth, accounts, dashboard, API layers end-to-end.}
      \resumeItem{Repo: \href{https://github.com/d3Par1/Coursework_Web}{github.com/d3Par1/Coursework\_Web}}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Telegram Bots} $|$ \emph{Python, aiogram / python-telegram-bot, SQLite}}{2025--Present}
    \resumeItemListStart
      \resumeItem{Built several Telegram bots exploring command handlers, inline keyboards, FSM (finite-state machines), and webhook deployment.}
      \resumeItem{Practiced async Python (\texttt{asyncio}), HTTP integration with external APIs, persistent state via SQLite.}
      \resumeItem{Demonstrates rapid prototyping skills, comfort with conversational interfaces, end-to-end ownership of a small backend product.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Roblox Grinding Simulator} $|$ \emph{Lua, Vide reactive UI, Blender (3D assets)}}{2025--Present}
    \resumeItemListStart
      \resumeItem{Solo-developed gameplay loop, inventory, shop systems demonstrating real-time state management.}
      \resumeItem{Designed adaptive UI with cross-device scaling, reactive UI architecture (Vide).}
      \resumeItem{Created custom 3D assets and preview / marketing scenes in Blender — full ownership of code, UI, visual content.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{University Coursework — OOP \& System Software} $|$ \emph{C\#, C, C++}}{2025--2026}
    \resumeItemListStart
      \resumeItem{Designed object-oriented systems in C\# covering SOLID principles, design patterns, software architecture.}
      \resumeItem{Implemented low-level system programs in C: memory management, process scheduling, IPC primitives.}
      \resumeItem{Repo: \href{https://github.com/d3Par1/University-Repository}{github.com/d3Par1/University-Repository}}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Microcontroller Side Projects} $|$ \emph{C / C++, MicroPython, Arduino IDE}}{2025--Present}
    \resumeItemListStart
      \resumeItem{Hands-on experimentation with Raspberry Pi Pico W and ESP32 — GPIO, sensors, Wi-Fi connectivity.}
      \resumeItem{Adds breadth: comfort with hardware-software boundaries and rapid prototyping outside the web stack.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-12pt}

%-----------LEARNING ROADMAP-----------
\section{In Progress (2026 Full-Stack Roadmap)}
\begin{itemize}[leftmargin=0.15in, label={\small\textbullet}]
    \small{
      \item \textbf{TypeScript} --- migrating JavaScript projects to TS for type safety and DX.
      \item \textbf{React + Next.js} --- modern SPA / SSR, hooks, server components.
      \item \textbf{PostgreSQL} --- moving from SQLite to production-grade RDBMS, indexing, query planning.
      \item \textbf{Docker \& docker-compose} --- containerizing dev environments, multi-service local stacks.
      \item \textbf{Testing} --- Jest, Playwright, Supertest for end-to-end coverage.
      \item \textbf{CI / CD} --- GitHub Actions pipelines, automated deployment.
    }
\end{itemize}
\vspace{-12pt}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Igor Sikorsky Kyiv Polytechnic Institute (KPI)}{Sep. 2024 -- Jun. 2028 (expected)}
    {B.Sc. Software Engineering \, $|$ \, Group ТВ-43}{Kyiv, Ukraine}
    \resumeItemListStart
      \resumeItem{\textbf{Relevant coursework:} Web Programming, Object-Oriented Analysis \& Design, Software Engineering Components, Data Structures \& Algorithms, Operating Systems, System Software Architecture.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-12pt}

%-----------TRAININGS-----------
\section{Trainings \& Self-Directed Learning}
\begin{itemize}[leftmargin=0.15in, label={\small\textbullet}]
    \small{
      \item \textbf{Linux Basics} --- KodeKloud (online, 2024). Shell, file system, processes, networking basics.
      \item \textbf{Web Programming Foundations} --- KPI structured course (2025--2026). HTTP, REST, SSR, RDBMS.
      \item \textbf{Telegram Bot API \& async Python} --- self-paced, multiple side projects (2025--present).
      \item \textbf{Blender 3D modeling} --- self-paced via official tutorials and community resources (2024--present).
    }
\end{itemize}
\vspace{-12pt}

%-----------ADDITIONAL-----------
\section{Additional}
\begin{itemize}[leftmargin=0.15in, label={\small\textbullet}]
    \small{
      \item \textbf{Self-learner:} Comfortable picking up new languages, frameworks, tools from official documentation. Recently: Vide (reactive Lua framework), Telegram Bot API, Blender pipeline.
      \item \textbf{Multilingual collaborator:} Native Ukrainian, advanced English, intermediate French --- comfortable in international / remote teams.
      \item \textbf{Open to:} Internship $\cdot$ Working Student $\cdot$ Junior roles (Kyiv / Remote / Hybrid / International remote).
    }
\end{itemize}

\end{document}
