%==========================================================================
% Stepanenko Nazar — Embedded / Miltech Software Engineer (Junior) CV
% PDFLATEX-COMPATIBLE VERSION  (для тих, хто не може переключити компілятор)
%==========================================================================
%
% ⚠️  BEFORE COMPILING — REPLACE 3 PLACEHOLDERS:
%   1. Phone:    +380 63 XXX XX XX     →  твій реальний номер
%   2. LinkedIn: linkedin.com/in/your-handle  →  твій URL
%   3. Telegram: @your_handle          →  твій нік
%
% ✅  COMPILER: works with pdfLaTeX, XeLaTeX, AND LuaLaTeX.
%               На Overleaf просто натисни Recompile — за замовчуванням pdfLaTeX.
%==========================================================================

\documentclass[10pt,a4paper,sans]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{blue}

% Aggressive geometry — 1 page strict
\usepackage[scale=0.88, top=0.8cm, bottom=0.8cm, left=1.2cm, right=1.2cm]{geometry}
\setlength{\hintscolumnwidth}{2.7cm}

% pdfLaTeX UTF-8 + Cyrillic support (БЕЗ fontspec!)
\usepackage[utf8]{inputenc}
\usepackage[T2A,T1]{fontenc}
\usepackage[ukrainian,english]{babel}

% Icons — FontAwesome 5 works in pdfLaTeX too
\usepackage{fontawesome5}

% Tight spacing for 1-page fit
\usepackage{enumitem}
\setlist[itemize]{topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=1pt, leftmargin=*}

\renewcommand*{\sectionfont}{\large\mdseries\upshape}
\setlength{\parskip}{0.2em}

% Personal data
\name{Nazar}{Stepanenko}
\title{\faMicrochip\ Embedded Software Engineer (Junior) \quad \faShieldAlt\ Defense Tech-Oriented}
\address{Kyiv, Ukraine}{}{}

% Contact line — FontAwesome icons
\extrainfo{%
    \faPhone\ +380 63 XXX XX XX \quad
    \faEnvelope\ \href{mailto:gangsterstepa@gmail.com}{gangsterstepa@gmail.com} \\[0.8mm]
    \faGithub\ \href{https://github.com/d3Par1}{github.com/d3Par1} \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/your-handle}{linkedin.com/in/your-handle} \quad
    \faTelegram\ @your\_handle \\[0.8mm]
    \faGlobe\ \textbf{UA} native $\bullet$ \textbf{EN} C1 $\bullet$ \textbf{FR} B1--B2 $\bullet$ \textbf{DE} A1--A2
}

\begin{document}

% MANUAL HEADER — bulletproof, не залежить від \makecvtitle quirks moderncv
\begin{center}
    {\Huge\bfseries Nazar Stepanenko} \\[0.4em]
    {\large\color{color1} \faMicrochip\ Embedded Software Engineer (Junior) \quad \faShieldAlt\ Defense Tech-Oriented} \\[0.5em]
    {\small Kyiv, Ukraine} \\[0.4em]
    {\small%
        \faPhone\ +380 63 XXX XX XX \quad
        \faEnvelope\ \href{mailto:gangsterstepa@gmail.com}{gangsterstepa@gmail.com}%
    } \\[0.3em]
    {\small%
        \faGithub\ \href{https://github.com/d3Par1}{github.com/d3Par1} \quad
        \faLinkedin\ \href{https://www.linkedin.com/in/nazar-stepanenko}{linkedin.com/in/nazar-stepanenko} \quad
        \faTelegram\ @your\_handle%
    } \\[0.3em]
    {\small \faGlobe\ \textbf{UA} native $\bullet$ \textbf{EN} C1 $\bullet$ \textbf{FR} B1--B2 $\bullet$ \textbf{DE} A1--A2}
\end{center}
\vspace{0.3em}
\noindent{\color{color1}\rule{\linewidth}{0.5pt}}
\vspace{0.5em}

%-----------SUMMARY-----------
\section{\faUser\ Summary}
\cvitem{}{\small Computer Science student (2nd year, Igor Sikorsky KPI, group \foreignlanguage{ukrainian}{ТВ}-43) building toward \textbf{embedded systems and unmanned-platform software for defense applications}. Strong C/C++ and Python foundation, hands-on with Raspberry Pi Pico W and ESP32, full-stack web ownership shipped as coursework. Currently extending toward STM32 bare-metal, FreeRTOS, and MAVLink-based drone software.}

%-----------SKILLS-----------
\section{\faCogs\ Technical Skills}
\cvitem{\faCode\ Programming}{\small C / C++, Python, C\#, JavaScript / Node.js, Lua, SQL, HTML/CSS}
\cvitem{\faMicrochip\ Embedded}{\small Raspberry Pi Pico W, ESP32 (Wi-Fi/BLE), Linux (CLI, Bash), GPIO / UART / I\textsuperscript{2}C / SPI basics, RTOS concepts (learning)}
\cvitem{\faTools\ Tools}{\small Git, VS Code, CLion, CMake, PlatformIO, Arduino IDE, Docker (basic), Wireshark, Blender (3D)}
\cvitem{\faRocket\ Areas of Interest}{\small UAV / drone software, autonomous systems, sensor fusion, defense electronics, secure firmware}

%-----------PROJECTS-----------
\section{\faFolderOpen\ Projects}

\cventry{05/2025 -- Present}
        {\faMicrochip\ Microcontroller Hands-On Practice}
        {Self-directed}
        {Pico W \& ESP32}
        {\textit{C / C++, MicroPython, PlatformIO, Arduino IDE}}
        {\small Exploratory projects across 2 board families: GPIO, sensor reading (BMP280, OLED, IMU), Wi-Fi/BLE connectivity, basic peripheral drivers. Workflow practice: toolchain setup, flashing, serial debugging, datasheet reading. \textbf{Next:} STM32 bare-metal (HAL/CMSIS), FreeRTOS multi-task firmware.}

\cventry{09/2025 -- 04/2026}
        {\faChartLine\ Personal Finance Manager}
        {Coursework, team of 2}
        {KPI Web Programming}
        {\textit{Node.js, Express, SQLite (better-sqlite3), Bootstrap 5, Chart.js}}
        {\small Full-stack web app with 4 module domains: \textbf{auth} (bcrypt + sessions), \textbf{multi-account architecture}, \textbf{transactions REST API}, \textbf{Chart.js analytics dashboard}. Owned auth, accounts, dashboard, API end-to-end. Repo: \href{https://github.com/d3Par1/Coursework_Web}{\faGithub\ d3Par1/Coursework\_Web}}

\cventry{2025 -- Present}
        {\faRobot\ Telegram Bots in Python}
        {Side projects}
        {}
        {\textit{Python, aiogram / python-telegram-bot, asyncio, SQLite}}
        {\small Multiple bots covering command handlers, inline keyboards, FSM (finite-state machines), webhook deployment. Async Python (\texttt{asyncio}), HTTP integration with external APIs, persistent state in SQLite. End-to-end product ownership.}

\cventry{2024 -- 2026}
        {\faGraduationCap\ University Coursework — Systems \& OOP}
        {KPI}
        {}
        {\textit{C, C++, C\#}}
        {\small Low-level systems programming in C: memory management, process scheduling, IPC primitives. OOP design in C\#: SOLID, design patterns, software architecture. Repo: \href{https://github.com/d3Par1/University-Repository}{\faGithub\ d3Par1/University-Repository}}

%-----------EDUCATION-----------
\section{\faUniversity\ Education}
\cventry{09/2024 -- 06/2028}
        {B.Sc. Software Engineering}
        {Igor Sikorsky Kyiv Polytechnic Institute (KPI)}
        {Kyiv, Ukraine}
        {Group \foreignlanguage{ukrainian}{ТВ}-43}
        {\small Coursework: System Software Architecture, OOA \& D, Web Programming, Data Structures \& Algorithms, Operating Systems, Software Engineering Components.}

%-----------TRAININGS-----------
\section{\faCertificate\ Trainings \& Self-Learning}
\begin{itemize}
    \item[\faBookmark] \small \textbf{Linux Basics} --- KodeKloud (online course, 2024)
    \item[\faBookmark] \small \textbf{Web Programming} --- KPI structured course (2025--2026)
    \item[\faBookmark] \small \textbf{Telegram Bot API \& async Python} --- self-paced, multiple shipped bots
    \item[\faBookmark] \small \textbf{Microcontroller hands-on} --- Raspberry Pi Pico W and ESP32, self-paced
    \item[\faBookmark] \small \textbf{Blender 3D modeling} --- self-paced, custom assets for solo Roblox project
\end{itemize}

%-----------ROADMAP-----------
\section{\faRoad\ 2026 Learning Roadmap}
\begin{itemize}
    \item[\faChevronRight] \small \textbf{STM32 bare-metal} (HAL/CMSIS) $\bullet$ \textbf{FreeRTOS} multitasking $\bullet$ \textbf{MAVLink} parser in C
    \item[\faChevronRight] \small \textbf{PX4 + Gazebo} simulation $\bullet$ \textbf{ROS2} pub/sub fundamentals
\end{itemize}

%-----------FOOTER-----------
\vspace{0.3em}
\small\textbf{\faPaperPlane\ Open to:} Internship $\cdot$ Working Student $\cdot$ Junior roles \quad (Kyiv / Remote / Hybrid / EU remote)

\end{document}
