%==========================================================================
% Stepanenko Nazar — Full-Stack / Web Developer (Junior) CV
% PRODUCTION-READY VERSION (всі критичні і high-priority фікси з HR-аудиту)
%==========================================================================
%
% ⚠️  BEFORE COMPILING — REPLACE 3 PLACEHOLDERS:
%   1. Phone:    +380 63 XXX XX XX     →  твій реальний номер
%   2. LinkedIn: linkedin.com/in/your-handle  →  твій URL
%   3. Telegram: @your_handle          →  твій нік
%
% ⚠️  COMPILER:  XeLaTeX  (Overleaf:  Menu → Compiler → XeLaTeX)
%==========================================================================

\documentclass[10pt,a4paper,sans]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{green}

\usepackage[scale=0.88, top=0.8cm, bottom=0.8cm, left=1.2cm, right=1.2cm]{geometry}
\setlength{\hintscolumnwidth}{2.7cm}

\usepackage{fontspec}
\usepackage{polyglossia}
\setmainlanguage{english}
\setotherlanguage{ukrainian}
\setmainfont{Latin Modern Sans}

\usepackage{fontawesome5}

\usepackage{enumitem}
\setlist[itemize]{topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=1pt, leftmargin=*}

\renewcommand*{\sectionfont}{\large\mdseries\upshape}
\setlength{\parskip}{0.2em}

\firstname{Nazar}
\familyname{Stepanenko}
\title{\faCode\ Full-Stack / Web Developer (Junior)}
\address{Kyiv, Ukraine}{}{}

\extrainfo{%
    \faPhone\ +380 63 XXX XX XX \quad
    \faEnvelope\ \href{mailto:gangsterstepa@gmail.com}{gangsterstepa@gmail.com} \\[0.8mm]
    \faGithub\ \href{https://github.com/d3Par1}{github.com/d3Par1} \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/your-handle}{linkedin.com/in/your-handle} \quad
    \faTelegram\ @your\_handle \\[0.8mm]
    \faGlobe\ \textbf{UA} native $\bullet$ \textbf{EN} C1 $\bullet$ \textbf{FR} B1--B2 $\bullet$ \textbf{DE} A1--A2
}

\begin{document}

\makecvtitle
\vspace{-1.2em}

%-----------SUMMARY-----------
\section{\faUser\ Summary}
\cvitem{}{\small Computer Science student (2nd year, Igor Sikorsky KPI, group \textukrainian{ТВ}-43) building \textbf{production-style full-stack web applications} with Node.js, Express, and modern frontend tooling. Recently shipped a finance-management web app as team coursework, plus several Python side projects (Telegram bots, automation). Looking for an internship or working-student role to grow as a full-stack engineer in a product-driven team.}

%-----------SKILLS-----------
\section{\faCogs\ Technical Skills}
\cvitem{\faCode\ Programming}{\small JavaScript / Node.js, Python, C\#, C / C++, Lua, SQL, HTML, CSS}
\cvitem{\faServer\ Web \& Backend}{\small Express.js, REST API design, EJS, Bootstrap 5, Chart.js, SQL (SQLite) schema design, Authentication (bcrypt, sessions), Async Python (asyncio, aiogram)}
\cvitem{\faTools\ Tools}{\small Git, GitHub Actions (basic), npm/pnpm, VS Code, Postman, Docker (basic), Linux (CLI, Bash), Blender (3D)}
\cvitem{\faRocket\ Areas of Interest}{\small SaaS, fintech, dev tools, productivity products, e-commerce}

%-----------PROJECTS-----------
\section{\faFolderOpen\ Projects}

\cventry{09/2025 -- 04/2026}
        {\faChartLine\ Personal Finance Manager}
        {Coursework, team of 2}
        {KPI Web Programming}
        {\textit{Node.js, Express, SQLite (better-sqlite3), Bootstrap 5, EJS, Chart.js}}
        {\small Full-stack web app with 4 module domains: \textbf{auth} (bcrypt + sessions), \textbf{multi-account architecture}, \textbf{transactions REST API}, \textbf{Chart.js analytics dashboard with server-side aggregation}. Designed relational schema with referential integrity. Owned auth, accounts, dashboard, API end-to-end. Repo: \href{https://github.com/d3Par1/Coursework_Web}{\faGithub\ d3Par1/Coursework\_Web}}

\cventry{2025 -- Present}
        {\faRobot\ Telegram Bots in Python}
        {Side projects}
        {}
        {\textit{Python, aiogram / python-telegram-bot, asyncio, SQLite}}
        {\small Multiple bots covering command handlers, inline keyboards, FSM (finite-state machines), webhook deployment. Async Python, HTTP integration with external APIs, persistent state in SQLite. End-to-end product ownership: requirements → implementation → deployment.}

\cventry{2024 -- 2026}
        {\faGraduationCap\ University Coursework — OOP \& Systems}
        {KPI}
        {}
        {\textit{C\#, C, C++}}
        {\small OOP design in C\#: SOLID principles, design patterns, software architecture. Low-level systems in C: memory management, process scheduling, IPC primitives. Repo: \href{https://github.com/d3Par1/University-Repository}{\faGithub\ d3Par1/University-Repository}}

\cventry{05/2025 -- Present}
        {\faMicrochip\ Microcontroller Side Projects}
        {Self-directed}
        {Pico W \& ESP32}
        {\textit{C / C++, MicroPython}}
        {\small Hands-on with Pico W and ESP32: GPIO, sensors, Wi-Fi connectivity. Adds breadth — comfort with hardware-software boundaries and rapid prototyping outside the web stack.}

%-----------EDUCATION-----------
\section{\faUniversity\ Education}
\cventry{09/2024 -- 06/2028}
        {B.Sc. Software Engineering}
        {Igor Sikorsky Kyiv Polytechnic Institute (KPI)}
        {Kyiv, Ukraine}
        {Group \textukrainian{ТВ}-43}
        {\small Coursework: Web Programming, Object-Oriented Analysis \& Design, Software Engineering Components, Data Structures \& Algorithms, Operating Systems, System Software Architecture.}

%-----------TRAININGS-----------
\section{\faCertificate\ Trainings \& Self-Learning}
\begin{itemize}
    \item[\faBookmark] \small \textbf{Linux Basics} — KodeKloud (online course, 2024)
    \item[\faBookmark] \small \textbf{Web Programming} — KPI structured course (2025--2026)
    \item[\faBookmark] \small \textbf{Telegram Bot API \& async Python} — self-paced, multiple shipped bots
    \item[\faBookmark] \small \textbf{Blender 3D modeling} — self-paced, custom assets for solo Roblox project
    \item[\faBookmark] \small \textbf{Microcontroller hands-on} — Pico W and ESP32, self-paced
\end{itemize}

%-----------ROADMAP-----------
\section{\faRoad\ 2026 Learning Roadmap}
\begin{itemize}
    \item[\faChevronRight] \small \textbf{TypeScript} migration $\bullet$ \textbf{React + Next.js} $\bullet$ \textbf{PostgreSQL} (indexing, query planning)
    \item[\faChevronRight] \small \textbf{Docker} multi-service compose $\bullet$ \textbf{Testing} (Jest, Playwright) $\bullet$ \textbf{CI/CD} (GitHub Actions)
\end{itemize}

%-----------FOOTER-----------
\vspace{0.3em}
\small\textbf{\faPaperPlane\ Open to:} Internship $\cdot$ Working Student $\cdot$ Junior roles \quad (Kyiv / Remote / Hybrid / EU remote)

\end{document}
